### 2019-01-18 micro3_2.tex
Micro

Since the solution should be interior that means that $c_1(w) = p_1, c_2(w) = p_2$. Hence, 
\begin{align*}
\frac{c_1(w)}{c_2(w)} = \frac{p_1}{p_2}\\
\left(\frac{w_1}{w_2}\right)^{1/2} = \sqrt{3}\\
w_1 = 3w_2\\
\end{align*}
Plugging it into $c_1(w) = p_1$ one can obtain:
\begin{align*}
4w_2 = 4 \to w_2 = 1, w_1 = 3\\
\end{align*}
Now let us find demand vectors for factors:
\begin{align*}
a_1(w) = \begin{pmatrix}
\frac{\partial c_1(w)}{\partial w_1}\\
\frac{\partial c_1(w)}{\partial w_2}
\end{pmatrix} = \begin{pmatrix}
\left(\frac{3w_2}{w_1}\right)^{1/4}\\
\left(\frac{w_1}{3w_2}\right)^{3/4}
\end{pmatrix} = \begin{pmatrix}
1\\
1
\end{pmatrix}\\
a_2(w) = \begin{pmatrix}
\frac{\partial c_2(w)}{\partial w_1}\\
\frac{\partial c_2(w)}{\partial w_2}
\end{pmatrix} = \begin{pmatrix}
\left(\frac{w_2}{3w_1}\right)^{3/4}\\
\left(\frac{3w_1}{w_2}\right)^{1/4}
\end{pmatrix} = \begin{pmatrix}
\dfrac{1}{\sqrt{27}}\\
\\
\sqrt{3}
\end{pmatrix}\\
\end{align*}
Since
\begin{align*}
\frac{a_{11}}{a_{21}} = 1 > \frac{\bar{z_1}}{\bar{z_2}} = \frac{1+3\sqrt{3}}{3\sqrt{3}(1 + \sqrt{3})} = \frac{8 - 2\sqrt{3}}{6\sqrt{3}} > \frac{a_{12}}{a_{22}} = \frac{1}{9}
\end{align*}
that means that solution is indeed interior.
To find the optimal output level $(q_1^*, q_2^*)$ we need the market clearing condition to be satisfied, i.e. we need to solve the following linear system:
\begin{align*}
q_1 \begin{pmatrix}
1\\
1
\end{pmatrix} + q_2 \begin{pmatrix}
\frac{1}{\sqrt{27}}\\
\sqrt{3}
\end{pmatrix} = \begin{pmatrix}
1 + \frac{1}{3\sqrt{3}}\\
1 + \sqrt{3}
\end{pmatrix}
\end{align*}
and the solution is obviously $q_2^* = 1, q_1^* = 1$. Thus, prices for factors are $w = (3, 1)$ and the equilibrium factors' allocation is:
\begin{align*}
\begin{pmatrix}
1\\
1
\end{pmatrix}, \begin{pmatrix}
\frac{1}{3\sqrt{3}}\\
\sqrt{3}
\end{pmatrix}
\end{align*}
\end{document}

>>>>

Since the solution should be interior that means that $c_1(w) = p_1, c_2(w) = p_2$. Hence, 
\begin{align*}
\frac{c_1(w)}{c_2(w)} = \frac{p_1}{p_2}\\
\left(\frac{w_1}{w_2}\right)^{1/2} = \sqrt{3}\\
w_1 = 3w_2\\
\end{align*}
Plugging it into $c_1(w) = p_1$ one can obtain:
\begin{align*}
4w_2 = 4 \to w_2 = 1, w_1 = 3\\
\end{align*}
Now let us find demand vectors for factors:
\begin{align*}
a_1(w) = \begin{pmatrix}
\frac{\partial c_1(w)}{\partial w_1}\\
\frac{\partial c_1(w)}{\partial w_2}
\end{pmatrix} = \begin{pmatrix}
\left(\frac{3w_2}{w_1}\right)^{1/4}\\
\left(\frac{w_1}{3w_2}\right)^{3/4}
\end{pmatrix} = \begin{pmatrix}
1\\
1
\end{pmatrix}\\
a_2(w) = \begin{pmatrix}
\frac{\partial c_2(w)}{\partial w_1}\\
\frac{\partial c_2(w)}{\partial w_2}
\end{pmatrix} = \begin{pmatrix}
\left(\frac{w_2}{3w_1}\right)^{3/4}\\
\left(\frac{3w_1}{w_2}\right)^{1/4}
\end{pmatrix} = \begin{pmatrix}
\dfrac{1}{\sqrt{27}}\\
\\
\sqrt{3}
\end{pmatrix}\\
\end{align*}
Since
\begin{align*}
\frac{a_{11}}{a_{21}} = 1 > \frac{\bar{z_1}}{\bar{z_2}} = \frac{1+3\sqrt{3}}{3\sqrt{3}(1 + \sqrt{3})} = \frac{8 - 2\sqrt{3}}{6\sqrt{3}} > \frac{a_{12}}{a_{22}} = \frac{1}{9}
\end{align*}
that means that solution is indeed interior.
To find the optimal output level $(q_1^*, q_2^*)$ we need the market clearing condition to be satisfied, i.e. we need to solve the following linear system:
\begin{align*}
q_1 \begin{pmatrix}
1\\
1
\end{pmatrix} + q_2 \begin{pmatrix}
\frac{1}{\sqrt{27}}\\
\sqrt{3}
\end{pmatrix} = \begin{pmatrix}
1 + \frac{1}{3\sqrt{3}}\\
1 + \sqrt{3}
\end{pmatrix}
\end{align*}
and the solution is obviously $q_2^* = 1, q_1^* = 1$. Thus, prices for factors are $w = (3, 1)$ and the equilibrium factors' allocation is:
\begin{align*}
\begin{pmatrix}
1\\
1
\end{pmatrix}, \begin{pmatrix}
\frac{1}{3\sqrt{3}}\\
\sqrt{3}
\end{pmatrix}
\end{align*}

\section*{Problem 2}
Suppose that as a function of factor prices $w = (w_1, w_2) >> 0$, the firms' cost for producing
one unit of output are as follows:
\begin{align*}
c_1(w) = \left(\frac{w_1}{2/3}\right)^{2/3}\left(\frac{w_2}{1/3}\right)^{1/3}\\
c_2(w) = \left(\frac{w_1}{1/2}\right)^{1/2}\left(\frac{w_2}{1/2}\right)^{1/2}
\end{align*}
Let
\begin{align*}
p_1 = \frac{6}{2^{\frac{2}{3}}}\text{ and } p_2 = 3
\end{align*}
be the unit price of the firms' outputs, respectively. Furthermore, assume that the total
endowment of the two factors are given by $\bar{z_1} = 2$ and $\bar{z_2} = 1$. Find the factor prices and
allocation in an equilibrium in which firm 2 shuts down. Verify that the firms' decisions are
truly optimal given the factor prices you determined.

As in previous exercise:
\begin{align*}
\frac{c_1(w)}{c_2(w)} = \frac{p_1}{p_2}\\ \frac{6}{2^{\frac{2}{3}}}\left(\frac{w_1}{w_2}\right)^{1/6} = \frac{6}{2^{\frac{2}{3}}3}\\
w_2 = 3^6w_1
\end{align*}
Now let us find the demand for factors:
\begin{align*}
a_1(w) = \begin{pmatrix}
\frac{\partial c_1(w)}{\partial w_1}\\
\frac{\partial c_1(w)}{\partial w_2}
\end{pmatrix} = \begin{pmatrix}
\left(\frac{2w_2}{w_1}\right)^{1/3}\\
\left(\frac{w_1}{2w_2}\right)^{2/3}
\end{pmatrix} = \begin{pmatrix}
2^{\frac{1}{3}}9\\
\frac{1}{2^{\frac{2}{3}}81}
\end{pmatrix}\\
a_2(w) = \begin{pmatrix}
\frac{\partial c_2(w)}{\partial w_1}\\
\frac{\partial c_2(w)}{\partial w_2}
\end{pmatrix} = \begin{pmatrix}
\left(\frac{w_2}{w_1}\right)^{1/2}\\
\left(\frac{w_1}{w_2}\right)^{1/2}
\end{pmatrix} = \begin{pmatrix}
27\\
\\
\frac{1}{27}
\end{pmatrix}\\
\frac{a_{11}}{a_{21}} = 2\cdot 3^6 > \frac{a_{12}}{a_{22}} = 3^6 > \frac{\bar{z_1}}{\bar{z_2}} = 2
\end{align*}
That means that in the equilibrium firm 1 should shut down.

\section*{Problem 3}
Suppose that for $w = (w_1, w_2) >> 0$, \begin{align*}
a_{11} = \frac{2}{3w_1}\left(\frac{w_1}{2/3}\right)^{2/3}\left(\frac{w_2}{1/3}\right)^{1/3}\\
a_{21} = \frac{2}{3w_2}\left(\frac{w_1}{2/3}\right)^{2/3}\left(\frac{w_2}{1/3}\right)^{1/3}\\
a_{12} = 
\end{align*}
\end{document}
